
\abstract{Sequential Pattern Mining is a popular research domain due to its increasing range of applications. In this article, we have introduced a new tree-based solution to the sequential pattern mining problem, including two sets of novel solutions for static and incremental sequential databases. We have proposed two new structures, \textit{SP-Tree} and \textit{IncSP-Tree} and designed two efficient algorithms, \textit{Tree-Miner} and \textit{IncTree-Miner} to mine the complete set of sequential patterns from static and incremental databases. Our proposed novel structures provide an efficient manner to store the complete sequential database, so they hold the ``build-once-mine-many" property and give scope to perform interactive mining. Additionally, we have proposed a new breadth-first based support counting technique, which helps detect a pattern's infrequency at an early stage and we have introduced a heuristic pruning strategy to reduce pattern search space. We have also designed a new pattern storage structure BPFSP-Tree to store the frequent patterns during successive iterations in incremental mining to reduce the number of database scans and to remove the infrequent patterns efficiently. A novel structure named Sequence Summarizer is also introduced to efficiently calculate and update the co-occurrence information of the items, especially in an incremental environment. Experimental results over various real-life and synthetic datasets demonstrate the efficiency of our work in comparison with the related state-of-the-art approaches.}
